Staged Abstract Interpreters

### 2018-11-17 paper/60_eval.tex
more eval

\subsection{Performance}
We performed our 
For each benchmark program, we ran our prototype abstract interpreters, both unstaged and staged.

>>>>

\subsection{Performance}
All of our evaluation benchmarks were performed on an Ubuntu 16.04 LTS (Linux 4.4.0) machine 
with 4 Intel(R) Xeon(R) Platinum 8168 CPUs running at 2.7GHz with a total of 3 TiB of RAM.
Although we were using an environment with 96 cores and 192 threads, we used only
one single thread for all the benchmark programs we run.

For each benchmark program, we ran our prototype abstract interpreters, both unstaged and staged.
\todo{Figure show data.}
